Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Remove informal expression

Knowing the interpolation method, the interpolation degree (number of points in the table) must be decided.
Obviously, using more points results in better accuracy, but also more computation time.
Then, a trade-off between performance and accuracy must be determined.
With this aim, the \textit{multi-objective optimization} method is used.

>>>>

Knowing the interpolation method, the interpolation degree $d$ (number of points in the table) must be decided.
Note, that using more points results in better accuracy, but also more computation time.
Then, a trade-off between performance and accuracy must be determined.
With this aim, the \textit{multi-objective optimization} method is used.
